Testing production scenarios for (anti-)(hyper-)nuclei with multiplicity-dependent measurements at the LHC

### 2019-03-31 EPIPHANY2019proceedings/Bellini_Epiphany2019_proc.tex
Thermal+blast wave finished

\subsection{Thermal + blast-wave model} 
Thermal-statistical models~\cite{Andronic:2010qu, Andronic:2017} have been successful in describing the production of light \mbox{(anti-)}(hyper-)nuclei across a wide range of energies in AA collisions, including production at the LHC. 
In this approach, particles are produced from a fireball in thermal equilibrium with temperatures of $T_{chem} \approx$ 156 MeV. 
Particle yields are derived from the partition function assuming a Grand Canonical ensemble\footnote{Extensions to small systems employ a canonical ensemble partition function to account for the exact conservation of quantum numbers in a finite size system, see for instance~\cite{Vovchenko:2018fiy}.} and they depend only on the mass of the particle and the temperature of chemical freeze-out, d$N$/d$y\propto$~exp$(-m/T_{\mathrm{chem}})$.
The thermal model cannot -- alone -- be compared to the \pt-dependent coalescence description because it provides only predictions for \pt-integrated yields. 
A thermal particle production implies a Boltzmann distribution of the momenta only for a static source, which is not the case of the rapidly expanding system produced in heavy-ion collisions. 
The thermal model (i.e. the GSI-Heidelberg implementation we have considered here) needs to be complemented by a hydrodynamic description of the rapidly expanding source. 
To that end, we use the Blast-Wave model~\cite{Schnedermann:1993ws}, which has been proven to describe reasonably well the measured momentum distributions of protons~\cite{Abelev:2013vea}. 
Our ``thermal+blast-wave'' approach results from the combination of the two models: the \pt-dependence is modelled by the blast-wave whereas the normalisation (i.e. the \pt-integrated yield) is taken from the thermal model predictions.

\section{Comparison with data} \label{sec:results}

>>>>

\subsection{Thermal + blast-wave model} 
Thermal-statistical models~\cite{Andronic:2010qu, Andronic:2017} have been successful in describing the production of light \mbox{(anti-)}(hyper-)nuclei across a wide range of energies in AA collisions, including production at the LHC. 
In this approach, particles are produced from a fireball in thermal equilibrium with temperatures of $T_{chem} \approx$ 156 MeV. 
Particle yields are derived from the partition function assuming a Grand Canonical ensemble\footnote{Extensions to small systems employ a canonical ensemble partition function to account for the exact conservation of quantum numbers in a finite size system, see for instance~\cite{Vovchenko:2018fiy}.} and they depend only on the mass of the particle and the temperature of chemical freeze-out, d$N$/d$y\propto$~exp$(-m/T_{\mathrm{chem}})$.
The thermal model cannot -- alone -- be compared to the \pt-dependent coalescence description because it provides only predictions for \pt-integrated yields. 
A thermal particle production implies a Boltzmann distribution of the momenta only for a static source, which is not the case of the rapidly expanding system produced in heavy-ion collisions. 
The thermal model (i.e. the GSI-Heidelberg implementation we have considered here) needs to be complemented by a hydrodynamic description of the rapidly expanding source. 
To that end, we use the Blast-Wave model~\cite{Schnedermann:1993ws}, which has been proven to describe reasonably well the measured momentum distributions of protons~\cite{Abelev:2013vea}. 
Our ``thermal+blast-wave'' approach results from the combination of the two models: the \pt-dependence is modelled by the blast-wave whereas the normalisation (i.e. the \pt-integrated yield) is taken from the thermal model predictions.
In particular, to shape the (hyper-)nucleus transverse momentum distributions we use the blast-wave parameters obtained from the simultaneous fit to pion, kaon and proton spectra measured in \PbPb~collisions by ALICE for several centralities/multiplicities and reported in~\cite{Abelev:2013vea}. We therefore inherit the multiplicity-dependence of the radial expansion of the system from the measurements. The object size does not enter in the formulation of the blast-wave model. 
In our thermal+blast-wave model, for each centrality/multiplicity class, the coalescence parameter is extracted according to Eq.~\ref{eq:BA} (as done for data) from the predicted (hyper-)nucleus spectrum and the proton spectrum measured by ALICE~\cite{Abelev:2013vea}.

\section{Results and discussion} \label{sec:results}
As discussed in the previous sections, the coalescence model describe the coalescence parameter
